---
title: "Neo4r"
description: |
  neo4j movie database example
author:
  - name: Bea Hernández
date: "`r Sys.Date()`"
output: radix::radix_article
params:
  user: 'neo4j'
  pass: 'root'
---

## Install dependencies

Neo4r is already [in CRAN](https://cran.r-project.org/web/packages/neo4r/) but I prefer the GitHub version which has faster updates.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = F, warning = F, echo = T)
```

```{r load_libraries}

if(!require(neo4r)){
    remotes::install_github("neo4j-rstats/neo4r")
    library(neo4r)
}

if(!require(visNetwork)){
    install.packages("visNetwork")
    library(visNetwork)
}

if(!require(dplyr)){
    install.packages("dplyr")
    library(dplyr)
}
```

*neo4r* is compatible with the **pipe** grammar but loading *magrittr* and/or *dplyr* is not necesary.

## Set your connection

I already have the movie database loaded on my neo4j database, so I just need to open my connection:

```{r open_connection}
con <- neo4j_api$new(url = "http://localhost:7474", 
                       user = params$user, password = params$pass)
con$ping()
```

```{r connection, echo = T}
con$get_version()
con$get_labels()
con$get_relationships()
```

## Let's query 

While I do this I'm watching The Godfather, so let's see what we find.

```{r, eval=F}
"MATCH (m:Movie {title: 'The Godfather'}) RETURN m" %>%
  call_neo4j(con)
```

There's nothing! We better import some *The Godfather* movies then:

```{r import_thegodfather}
send_cypher('../data/thegodfather.cypher', con)
```

After this we can look for some *Godfatherish* things. 